investigation of new soccerway game layout

## packages

```{r}
library(tidyverse)
library(rvest)
```

## play

```{r}
urls <- tribble(
  ~note, ~url,
  "postponed" , "https://int.soccerway.com/matches/2020/06/22/south-america/copa-america/australia/bolivia/3189349/",
  "penalties" , "https://int.soccerway.com/matches/2020/06/20/lithuania/cup/utenis-utena/fk-atlantas/3277935/",
  "normal"    , "https://int.soccerway.com/matches/2020/01/22/spain/copa-del-rey/ud-ibiza/futbol-club-barcelona/3208733/",
  "cancelled" , "https://int.soccerway.com/matches/2020/05/09/france/ligue-1/stade-de-reims/amiens-sporting-club-football/3030898/",
  "penalties" , "https://int.soccerway.com/matches/2020/01/04/france/coupe-de-france/sable-fc/pau-football-club/3190891/",
  "not played", "https://int.soccerway.com/matches/2020/06/21/costa-rica/liga-de-ascenso/sporting-san-jose/ad-escazucena/3277921/",
  "normal"    , "https://int.soccerway.com/matches/2020/06/22/england/premier-league/manchester-city-football-club/burnley-fc/3029367/",
  "extra time", "https://int.soccerway.com/matches/2020/03/03/england/fa-cup/reading-fc/sheffield-united-fc/3221322/",
  "extra time", "https://int.soccerway.com/matches/2020/06/22/england/league-two/exeter-city-fc/colchester-united-fc/3277183/",
  "not played", "https://int.soccerway.com/matches/2020/07/03/england/championship/charlton-athletic-football-club/millwall-fc/3036534/"
)
urls
```

```{r}
urls %>% 
  mutate(html=map(url, ~read_html(.))) -> d
d
```




xpaths

```{r}
xpaths <- c(
  '//*[@id="page_match_1_block_match_info_5"]/div/div/div[2]/span', # postponed
  '//*[@id="page_match_1_block_match_info_5"]/div/div/div[2]/h3/span[1]', # FT (with P)
  '//*[@id="page_match_1_block_match_info_5"]/div/div/div[2]/h3/span[2]', # P on left
  '//*[@id="page_match_1_block_match_info_5"]/div/div/div[2]/h3', # the whole score block
  '//*[@id="page_match_1_block_match_info_5"]/div/div/div[2]' # hmm: it's all here, just needs finding
)
xpaths
```

```{r}
get_text <- function(h, xp) {
    h %>% html_nodes(xpath = xp) %>% html_text() %>% 
    str_split("\n") %>% pluck(1) %>% str_trim()
}
get_score <- function(x) {
  x %>% str_extract("^[0-9]+ - [0-9]+$") %>% na.omit() -> w
  x %>% str_extract("^[0-9]+:[0-9]+$") %>% na.omit() -> k
  case_when(
    length(w) > 0 ~ w[1],
    length(k) > 0 ~ k[1],
    TRUE          ~ ""
  )
}

```

```{r}
d %>% mutate(r=row_number()) %>% 
  mutate(v = map(html, ~get_text(., xpaths[5]))) -> vv
vv %>% unnest(v) %>% 
  select(r, note, v)
```

```{r}
vv %>% select(r, note, v) %>% 
  mutate(is_postponed = map_lgl(v, ~any(str_detect(., "^Postponed$")))) %>% 
  mutate(is_penalties = map_lgl(v, ~any(str_detect(., "^P$")))) %>% 
  mutate(is_extra = map_lgl(v, ~any(str_detect(., "^E$")))) %>% 
  mutate(score = map_chr(v, ~get_score(.))) %>% 
  mutate(is_done = map_lgl(v, ~any(str_detect(., "FT|AET")))) %>% 
  mutate(stat = case_when(
    is_postponed ~ "P",
    !is_done     ~ "",
    is_penalties ~ "FT-Pen",
    is_extra     ~ "FT-E",
    TRUE         ~ "FT"
  )) 
```

```{r}
vv %>% pluck("v", 6) -> x
x
```



```{r}
any(str_detect(x, "^Postponed$"))
str_extract(x, "^[0-9]+ - [0-9]+$") %>% na.omit()
get_score(x)
```


notes

postponed: item 5 is Postponed
penalties: item 8 is score, 7 and 9 are P, 6 is FT. Or, 5 is AET, the rest back 1
normal: item 8 is score, 6 is FT, 15 is half-time score
cancelled: all blank (5 items)
extra time: 5 is AET, 7 is score, 6 and 8 are E, 14 is full-time score
not played yet (but scheduled): 2 is KO, 6 is ko time (eg 22:00), may be others like an agg

## jottings

```{r}
url_to_game=function(url) {
  
  retrieved_time <- now()
  read_html(url) -> the_match
  Sys.sleep(0.5)
  
  # match number
  
  url %>% str_split("/") %>% pluck(1, 12) %>% as.numeric() -> match_number
  
  
  # team names and score
  
  xpaths <- c('//*[@id="page_match_1_block_match_info_5"]/div/div/div[1]/a[2]', # home team
              '//*[@id="page_match_1_block_match_info_5"]/div/div/div[3]/a[2]', # away tean
              '//*[@id="page_match_1_block_match_info_5"]/div/div/div[2]/h3/span[1]', # match status
              '//*[@id="page_match_1_block_match_info_5"]/div/div/div[2]/h3/text()', # score
              '//*[@id="page_match_1_block_match_info_5"]/div/div/div[5]/a[2]', # league
              '//*[@id="page_match_1_block_match_info_5"]/div/div/div[5]') # details, ko date and time
  
  the_match %>% html_nodes(xpath = xpaths[1]) %>% 
    html_text() -> t1_name
  the_match %>% html_nodes(xpath = xpaths[1]) %>% 
    html_attr("href") %>% 
    str_split("/") %>% pluck(1, 5) %>% as.numeric() -> t1_id
  the_match %>% html_nodes(xpath = xpaths[2]) %>% 
    html_text() -> t2_name
  the_match %>% html_nodes(xpath = xpaths[2]) %>% 
    html_attr("href") %>% 
    str_split("/") %>% pluck(1, 5) %>% as.numeric() -> t2_id
  
  the_match %>% html_nodes(xpath=xpaths[3]) %>% html_text() -> status
  
  the_match %>% html_nodes(xpath=xpaths[4]) %>% html_text() %>% 
    pluck(2) %>% str_remove_all("\n") %>% 
    str_trim() -> score
  
  the_match %>% html_nodes(xpath=xpaths[5]) %>% 
    html_text() -> league_name
  
  the_match %>% html_nodes(xpath=xpaths[5]) %>% 
    html_attr("href") %>% 
    str_split("/") -> comp_info
  
  comp_info %>% pluck(1, 7) %>% 
    str_remove("r") %>% as.numeric() -> league_number
  
  comp_info %>% pluck(1, 3) -> country
  
  the_match %>% html_nodes(xpath=xpaths[6]) %>% 
    html_nodes("span") %>% html_attr("data-value") %>% 
    enframe() %>% filter(!is.na(value)) %>% pull() %>% as.numeric() %>% 
    as_datetime(tz="America/Toronto") -> kickoff
  
  pb$tick()
  
  # tibble
  
  tibble(match=match_number,
         t1=t1_id,
         t2=t2_id,
         comp=league_number,
         country=country,
         t1_name=t1_name,
         t2_name=t2_name,
         score=score,
         comp_name=league_name,
         time_stamp=kickoff,
         retrieved=retrieved_time,
         stat=status
  )
}

```

