 idea: get matches from eg today *by game*

## startup

```{r}
library(tidyverse)
library(dplyr, warn.conflicts = F)
library(rvest)
library(lubridate)
library(progress)
library(janitor)
library(conflicted)
conflict_prefer("pluck", "purrr")
conflict_prefer("filter", "dplyr") 
source("functions.R")
source("new_from_here.R")
```


## get today's leagues

### set up playoff leagues with urls

needs columns `comp_id` and `league_url` 

```{r}
playoffs <- tribble(
  ~comp_id, ~league_url,
  54897, "https://int.soccerway.com/national/armenia/premier-league/20192020/championship-round/r54897/",
  54898, "https://int.soccerway.com/national/armenia/premier-league/20192020/relegation-round/r54898/",
  54161, "https://int.soccerway.com/national/austria/bundesliga/20192020/championship-round/r54161/",
  54165, "https://int.soccerway.com/national/austria/bundesliga/20192020/relegation-round/r54165/",
  54088, "https://int.soccerway.com/national/bulgaria/a-pfg/20192020/relegation-round/r54088/",
  54083, "https://int.soccerway.com/national/bulgaria/a-pfg/20192020/championship-round/r54083/",
  54505, "https://int.soccerway.com/national/czech-republic/czech-liga/20192020/championship-round/r54505/",
  54510, "https://int.soccerway.com/national/czech-republic/czech-liga/20192020/relegation-round/r54510/",
  54281, "https://int.soccerway.com/national/denmark/superliga/20192020/championship-round/r54281/",
  54286, "https://int.soccerway.com/national/denmark/superliga/20192020/relegation-round/r54286",
  53558, "https://int.soccerway.com/national/greece/super-league/20192020/championship-round/r53558/",
  53559, "https://int.soccerway.com/national/greece/super-league/20192020/relegation-round/r53559/",
  53506, "https://int.soccerway.com/national/poland/ekstraklasa/20192020/relegation-round/r53506/",
  53504, "https://int.soccerway.com/national/poland/ekstraklasa/20192020/championship-round/r53504/",
  54244, "https://int.soccerway.com/national/romania/liga-i/20192020/championship-round/r54244/",
  54246, "https://int.soccerway.com/national/romania/liga-i/20192020/relegation-round/r54246/",
  53770, "https://int.soccerway.com/national/slovakia/super-liga/20192020/championship-round/r53770/",
  53772, "https://int.soccerway.com/national/slovakia/super-liga/20192020/relegation-round/r53772/",
  54066, "https://int.soccerway.com/national/ukraine/premier-league/20192020/championship-round/r54066/",
  54068, "https://int.soccerway.com/national/ukraine/premier-league/20192020/relegation-round/r54068/",
)
playoffs
```


```{r today}
# today <- strftime(today()+1, format="%Y/%m/%d")
# today 
# l <- leagues_from_date(today)
# l
# nrow(l)
# l %>% separate(league_url, into=c("a","b", "c", "d", "category", "country", "league1", "league2"), extra="drop") %>%
#   unite(league, league1, league2) %>%
#   select(country, league, comp_id) %>%
#   arrange(country, league) %>%
#  View("today's leagues")
days <- (-3):4
tibble(days) %>% mutate(thedate=strftime(today()+days, format = "%Y/%m/%d")) %>% 
  mutate(l=map(thedate, ~leagues_from_date(.))) %>% 
  unnest(l) %>% 
  group_by(comp_id) %>% 
  arrange(league_url) %>% 
  slice(1) %>% 
  select(comp_id, league_url) -> l
# View(l, "ll")
l %>% bind_rows(playoffs) -> l
nrow(l)
```

get match numbers for all these (all the matches on soccerway for all the leagues that are playing today)

```{r}
league_url_to_match_numbers_possibly <- possibly(league_url_to_match_numbers, otherwise=list())
pb <- progress_bar$new(format = " progress [:bar] :percent eta: :eta", total = nrow(l), width=50)
l %>% mutate(match_number=map(league_url, ~league_url_to_match_numbers_possibly(.))) %>% 
  unnest(match_number) -> m
# m %>% filter(comp_id==53499) %>% arrange(desc(date))
# View(m)
"m done"
```

save m

```{r}
write_rds(m, "m.rds")
```


## get games and m (can start from here)

```{r}
m <- read_rds("m.rds")
games <- read_rds("rds/games.rds")
nrow(games)
```


select games with results and anti-join to above

I want to get game details if: (i) the game doesn't exist at all in games; (ii) the game does exist and might have a result (which includes postponed)

## (i) in m but not in games at all (do this first)

```{r}
base="http://www.soccerway.com"
m %>% anti_join(games, by="match") %>% 
  mutate(match_url=str_c(base, match_url)) -> games_to_get
nrow(games_to_get)
pb <- progress_bar$new(format = " progress [:bar] :percent eta: :eta", 
                       total = nrow(games_to_get), width = 50)
games <- new_combine(games_to_get, "do not have")
nrow(games)
```

if empty, go back and get games again, then proceed to (ii) and (iii).

## (ii) game does exist, doesn't have a result, and might have a result now (I need the url and the timestamp)

this doesn't seem to get the ones like 2:1

```{r, might-have}
base="http://www.soccerway.com"
get_postponed <- "y"
games %>% filter(!str_detect(score, " - ")) %>% # there might be none of these
  filter(!str_detect(score, "Cancelled")) %>% 
  filter(!str_detect(score, "Postponed") | get_postponed=="y")  -> g 
m %>% inner_join(g, by="match") %>% 
  select(league_url, match_url, date, match, time_stamp) %>% 
  mutate(match_url=str_c(base, match_url)) %>% 
  filter((now()-time_stamp)/dhours(1)>2.5) %>% 
  # filter((now()-time_stamp)/ddays(1)<7) %>% # drop off after a week
  select(-time_stamp) -> games_to_get
nrow(games_to_get)
pb <- progress_bar$new(format = "pr [:bar] :percent eta: :eta", total = nrow(games_to_get), width = 50)
games <- new_combine(games_to_get, "new games")
nrow(games)
```

## (iii) games scheduled for the next little while



```{r, coming up}
base="http://www.soccerway.com"
games %>% filter(!str_detect(score, " - ")) %>% # there might be none of these
  filter(!str_detect(score, "Cancelled")) %>% 
  filter(!str_detect(score, "Postponed")) -> g
m %>% inner_join(g, by="match") %>% 
  select(match, country, comp_name, t1_name, t2_name, score, time_stamp) %>% 
  arrange(time_stamp) %>% 
  View("future games")
  # filter((now()-time_stamp)/ddays(1)<7) %>% # drop off after a week
  # select(-time_stamp) -> games_to_get
# ne
# View(games_to_get, "future games")
# pb <- progress_bar$new(format = " progress [:bar] :percent eta: :eta", total = nrow(games_to_get))
# games <- new_combine(games_to_get, "future games")
```

## (iv) remove results gotten too soon and reget

```{r}
base="http://www.soccerway.com"
games %>% filter(stat!="FT") %>% 
  filter(str_detect(score, " - ")) -> g
g
m %>% inner_join(g, by="match") %>% 
  select(league_url, match_url, date, match, time_stamp) %>% 
  mutate(match_url=str_c(base, match_url)) %>% 
  select(-time_stamp) -> games_to_get
nrow(games_to_get)
pb <- progress_bar$new(format = " progress [:bar] :percent eta: :eta", total = nrow(games_to_get))
games <- new_combine(games_to_get, "re-gotten games")
```



## (v) tidy up extraneous cols 



```{r}
games %>% distinct()
to_keep <- function(x) {
  x %>% discard(is.null) %>% 
    discard(is.na) -> y
  length(y) == length(x)
}

(length(names(games)))
games %>% select(where(~to_keep(.))) -> games
(length(names(games)))
nrow(games)
games %>% distinct(match, .keep_all = TRUE) -> games
nrow(games)
saveRDS(games,"rds/games.rds")
```




## jottings


### go from here (now a function)

```{r go-from-here}
url_to_game_possibly=possibly(url_to_game, otherwise=list())
pb <- progress_bar$new(format = " progress [:bar] :percent eta: :eta", total = nrow(games_to_get))
games_to_get %>% 
  mutate(match_info=map(match_url, ~url_to_game_possibly(.))) %>% 
  unnest(match_info, .name_repair="minimal") %>%
  select(-match_url, -date, -match1, -.name_repair, -league_url, -comp_id) -> mmm
"done go"
```

look at results (now a function also)

change partials to : (keep it to be safe, eg if match has been rescheduled later, and apparently complete score is only partial)        

```{r}
mmm %>% mutate(since=(retrieved-time_stamp)/dhours(1)) %>% 
  mutate(score=ifelse(since<2.5, str_replace(score, "-", ":"), score)) %>%   
  select(-since) -> mmm
mmm %>% mutate(status=case_when(
  str_detect(score, " - ") ~ "done",
  str_detect(score, " : ") ~ "in progress",
  TRUE                    ~ "scheduled"
  )) %>%
  arrange(status, time_stamp) %>% View("mmm")
```



combine with games

```{r combine}
games <- read_rds("rds/games.rds")
games <- combine2(games, mmm)
games %>% distinct(match, .keep_all = T) -> games
saveRDS(games,"rds/games.rds")
"done"
```







```{r}
read_html(url) %>% html_nodes("a") %>% html_attr("href") %>% 
  enframe() %>% filter(str_detect(value, "^/matches/")) %>%
  extract(value, into="match", regex="/([0-9]+)/$", remove=F, convert=T) %>% 
  drop_na(match) %>% 
  distinct(match, .keep_all = T) %>% 
  select(-name, match_url=value)
```

get match numbers for a league

```{r}
url <- l$league_url[17]
url
m <- league_url_to_match_numbers(url)
m
```

(ii) get ones that are in games and due. This has nothing to do with what we just did.


```{r}
today <- as.Date("2020-02-08")
games %>% filter(str_detect(score, " - ")) -> gs
m %>% anti_join(gs, by="match") %>% 
  mutate(match_url=str_c("http://www.soccerway.com", match_url)) -> games_to_get # I want to get future ones as well, or maybe not
games_to_get
```



### temporary sample of a few

```{r}
games_to_get_all <- games_to_get
games_to_get_all %>% sample_n(50) -> games_to_get
```

```{r}
want <- c(53497, 53866)
games_to_get %>% filter(comp_id %in% want) -> games_to_get
```

```{r}
games_to_get
```
