
## packages and prelim

```{r}
library(tidyverse)
library(lubridate)
library(rvest)
library(conflicted)
conflict_prefer("pluck", "purrr")
conflict_prefer("filter", "dplyr") 
source("functions.R")
source("new_from_here.R")
```

## get games

```{r}
games <- read_rds("rds/games.rds")
nrow(games)
```

```{r}
games
```

problem is that comp is recent  but games are old

this might need fixing directly:

```{r}
games %>% filter(comp==53268) %>%
  arrange(desc(time_stamp))
```

l, m from elsewhere

```{r}
l %>% mutate(z=1) %>% View("l")
View(m)
```

l is ok but m is not

here is where m comes from (don't run yet)

```{r}
league_url_to_match_numbers_possibly <- possibly(league_url_to_match_numbers, otherwise=list())
pb <- progress_bar$new(format = " progress [:bar] :percent eta: :eta", total = nrow(l))
l %>% mutate(match_number=map(league_url, ~league_url_to_match_numbers_possibly(.))) %>% 
  unnest(match_number) -> m
m
"m done"
```

so...

```{r}
url <- "https://www.soccerway.com/national/italy/serie-b/20192020/regular-season/r54637/"
pb <- progress_bar$new(format = " progress [:bar] :percent eta: :eta", total = 1)
league_url_to_match_numbers(url)
```

these are ok, so why are they wrong from before?

I might be able to fix games that are in wrong league by looking up any game, then substituting the game number I want at the end (this may work)
I need to return the correct comp number, by obtaining the league that the match was actually played in and substituting
(or, get that as part of getting the match)

```{r}
a_match_url <- "https://int.soccerway.com/matches/2018/10/06/mexico/liga-premier-serie-b/potosino/deportivo-cafessa/2859833/"
```

idea: change the match number and leave the rest of it the same
