---
title: "get league results from soccerway"
output: html_notebook
---

## packages

```{r}
library(tidyverse)
library(rvest)
library(lubridate)
library(glue)
library(conflicted)
conflict_prefer("pluck", "purrr")
conflict_prefer("filter", "dplyr") 
source("functions.R")
```

## get leagues and urls

```{r}
urls <- read_rds("~/Documents/odds/urls.rds")
urls %>% mutate(url=str_c(url, "matches/")) %>% 
  extract(url, into="id", regex="/r([0-9]+)/", remove=F, convert=T) -> urls
urls
urls %>% pull(id) -> the_leagues
```

```{r}
# View(urls)
```

combine these with all_url:

```{r}
urls %>% select(url, comp=id) %>% 
  mutate(url_short=str_replace(url, "^.*.soccerway.com", "")) %>% 
  extract(url_short, into=c("country", "league"), regex="^/[^/]*/([^/]*)/([^/]*)", remove=F) %>% 
  select(url=url_short, country, league, comp) -> odds_url
odds_url
old_urls <- read_rds("~/teaching/scoresway/all_url.rds") 
old_urls
old_urls %>% mutate(comp=as.integer(comp)) %>% 
  bind_rows(odds_url) %>% 
  distinct(comp, .keep_all = T) %>% 
  mutate(key=str_c(country, league)) %>% 
  mutate(key=str_replace_all(key, "-", "")) %>% 
  mutate(league=abbreviate(key, minlength = 4, method="both")) %>% 
  select(league, url, id=comp) -> all_leagues
all_leagues %>% pull(id) -> the_leagues
```



## check for comps with upcoming games (that are prior to now with : or Postponed)

get the actual games first


get this from `games`: get games that are done and not too old (that ought to still be on matches)

```{r}
games <- read_rds("rds/games.rds")
```


games which are due (or, better, leagues with due games) finished in last day

maybe get *all* comps and score their urls somewhere

```{r, paged.print=F}
games %>% 
  filter(comp %in% the_leagues) %>% # think about removing this, but will need to have table of urls by league
  filter(time_stamp+2.5*60*60<now()) %>% # games that have finished
  filter(time_stamp>now()-1.25*24*60*60) %>% # go back one day (for further back, catch postponed games below); actually 1.25 days just in case
  # filter(str_detect(score, ":") | str_detect(score, "Postponed")) -> to_get
  filter(str_detect(score, ":")) -> to_get # don't get postponed ones here
to_get %>% distinct(comp) %>% pull(comp) -> leagues_to_get
to_get %>% distinct(comp) %>% 
  left_join(all_leagues, by=c("comp"="id")) %>% 
  arrange(url) %>% print(n=Inf)
```

catching up with postponed games

```{r, paged.print=F}
games %>% 
  filter(comp %in% the_leagues) %>% 
  filter(time_stamp<now()-1*24*60*60) %>% # at least a day ago
  filter(time_stamp>now()-30*24*60*60) %>% # go back a month (30 days)
  filter(str_detect(score, ":") | str_detect(score, "Postponed")) -> to_get
to_get %>% distinct(comp) %>% pull(comp) -> leagues_to_get
to_get %>% distinct(comp) %>% 
  left_join(urls, by=c("comp"="id")) %>% 
  arrange(league) %>% print(n=Inf)
```



or, a random selection from all leagues


```{r, paged.print=F}
urls %>% sample_frac(0.02) %>% 
  pull(id) -> leagues_to_get
urls %>% filter(id %in% leagues_to_get)
```

leagues that have no future games

```{r, paged.print=F}
games %>% filter(time_stamp>now()) %>% distinct(comp) -> future_comps
urls %>% anti_join(future_comps, by=c("id"="comp")) %>% 
  filter(str_detect(url, "20192020")) %>% 
  filter(games>10) %>% 
  pull(id) -> leagues_to_get
leagues_to_get
length(leagues_to_get)
```


or, particular league(s) 

```{r}
wants <- c(53131, 53437, 53161, 53165, 53677, 53874, 54637, 53081, 52784, 53987, 54796, 53502, 54950, 53474)
# want %>% str_split(" ", simplify=T) %>% as.vector() -> wants
all_leagues %>% filter(id %in% wants) %>% pull(id) -> leagues_to_get
```


### grab some

```{r}
leagues_to_get
n_get <- 10
leagues_to_get <- sample(leagues_to_get, n_get)
# leagues_to_get
```




## get all game info for these leagues

to skip

```{r}
skip=c()
leagues_to_get <- leagues_to_get[!(leagues_to_get %in% skip)]
leagues_to_get <- leagues_to_get[leagues_to_get>50000]
```


occasionally there is value in getting them all (if there were no games before but now there are some)

here is get

```{r}
leagues_to_get
length(leagues_to_get)
league_url_to_game_info_possibly <- possibly(league_url_to_game_info, otherwise=list())
pb <- progress_estimated(length(leagues_to_get)) # old, use pb <- progress_bar$new(format = " progress [:bar] :percent eta: :eta", total = nrow(l))

all_leagues %>% filter(id %in% leagues_to_get) %>% 
  # slice(11:n()) %>%
  # sample_n(5) %>% 
  mutate(game_info=map(url, ~league_url_to_game_info_possibly(str_c("https://int.soccerway.com", .)))) -> w # check whether game timestamp was less than 2.5 hours ago; if so change score separator to :
write_rds(w, "w.rds")
bind_rows(w$game_info) -> mmm
# glue({format(now(), "%Y-%m-%d %H:%M:%S")}, ": Done")
beepr::beep(2)
msg=str_c("Matches: ", nrow(mmm))
# RPushbullet::pbPost("note", title="Scoresway dl complete", body=msg)
beepr::beep(2)
```



## list the games we got. (Hint: show me only the new ones)

Comment out filter line to include future games. And run this even if you don't intend to look at it (creating `mmm2`)


```{r}
# things are coming out double
mmm %>% 
  mutate(retr_after=(retrieved-time_stamp)/dhours(1)) %>% 
  mutate(score=ifelse(retr_after<2.5, str_replace(score, "-", ":"), score)) %>% 
  select(match, country, comp, comp_name, t1_name, t2_name, t1, t2, score, time_stamp, retrieved) -> mmm2
mmm2 %>% filter(str_detect(score, " - ")) %>% 
  distinct(match, .keep_all = T) %>% 
  filter(time_stamp<now()) %>% # comment
  arrange(desc(time_stamp)) -> d1
games %>% filter(!str_detect(score, " - ")) -> d2
d1 %>% semi_join(d2, by="match") -> mmx # rows of d1 also in d2
View(mmx, "mmm")
# mmm2 %>%
#   distinct(match, .keep_all=T) %>% 
#   filter(time_stamp<now()) %>% # comment out to get future games also
#   arrange(desc(time_stamp)) %>% View("mmm")
```




combine with games df

```{r}
games <- read_rds("rds/games.rds")
games <- combine2(games, mmm2)
games %>% distinct(match, .keep_all = T) -> games
saveRDS(games,"rds/games.rds")
```

## end ######################################################

## jottings

investigation

a real url and non-real url

```{r}
the_real_url <- "https://ca.soccerway.com/national/france/cfa-2/20192020/group-i/r55112/"
the_unreal_url <- "https://ca.soccerway.com/national/france/cfa-2/20192020/group-i/r66113/"
```

what does league_url_to_game_info return?

```{r}
d1=league_url_to_game_info(the_real_url)
d1
```

a data frame.

If it fails, I want something I can bind_rows with it:

```{r}
d2 <- league_url_to_game_info(the_unreal_url)
d2 <- list()
bind_rows(d1, d2)
```

try it

```{r}
league_url_to_game_info_possibly <- possibly(league_url_to_game_info, otherwise=list())
urls <- c(the_real_url, the_unreal_url)
enframe(urls) %>% 
  mutate(x=map(value, ~league_url_to_game_info_possibly(.))) -> ddd
ddd
bind_rows(ddd$x)
```




