# other stuff

### checking

```{r}
games %>% filter(comp==41514)
```

```{r}
games %>% filter(comp==41245) %>% group_by(t1) %>% 
  count(t1_name) %>% arrange(desc(n)) %>% top_n(1)
```


#### get a league update (example)

```{r}
games %>% filter(comp==41506) %>% filter(!str_detect(score," - ")) %>% get_games() -> xx
xx
```


## read from RDS if object lost/corrupted

```{r}
games=readRDS("rds/games.rds")
```



<!-- ## fill in missing countries -->

<!--  ```{r} -->
<!-- #xx=table_by_comp_id(732) -->
<!-- (xx=map_df(dc[ij],table_by_comp_id)) -->
<!-- xx %>% count(country,comp_name) %>% print(n=Inf) -->

<!-- dim(games) -->
<!-- games=combine(games,xx)  -->
<!-- games -->
<!-- saveRDS(games,"games.rds") -->

<!-- # get competition ids for several days and combine -->
<!-- # also need to think about getting list of matches (country is problem then: look up country later) -->


<!-- (games=combine(games,xx) ) -->
<!-- saveRDS(games,"games.rds") -->

<!-- league=41547 -->
<!-- (xx=table_by_id(league,"round")) # get latest page of results from scoresway -->

<!-- (m2=matches_in(games,league)) # matches in current database -->
<!-- (mm=missing_matches(games,league)) -->
<!-- (xx=get_game_numbers(mm)) -->
<!-- (xx=back_n(m2,300)) -->

<!-- # if I find games from another league, I've (probably) gone back far enough. Or if the first thing in xx is the same league,  -->
<!-- # I should keep going. -->

<!-- # get latest page for several "rounds" -->

<!-- ll=lgs$`2017` -->
<!-- (leagues=ll[!is.na(ll)]) -->
<!-- (xx=map_df(leagues,table_by_id,"round")) -->

<!-- second_divs=c() -->

<!-- (xx=back_n_league(39293,20,games)) -->
<!-- ij=1:20 -->
<!-- leagues[ij] -->
<!-- (xx=map_df(leagues[ij],back_n_league,25,games)) -->

<!-- # fill in missing: these are games that I already have, collecting results; this is good. -->
<!-- ``` -->







## fill in missing countries

```{r}
ll=lev2
ll=dc

n_back=10
tibble(id=ll) %>% mutate(first=map_dbl(id,first_match,games)) %>% 
  filter(!is.na(first)) %>% 
  mutate(matches=map## get upcoming games

get xx (games that I just got results for): this could stand to be shrunk to the games I actually *got* results for, not just the ones I might have done

```{bash}
rm rds/mci*.rds
rm rds/sched*.rds
```

```{r}
xx=readRDS("rds/xx.rds")
xx %>% filter(str_detect(score, " - ")) %>% 
  distinct(comp) %>% nrow()
```

these are the comps that just had games for which I have results, so they are ripe for getting new ones
if error here, likely no rows

```{r}
xx %>% filter(str_detect(score, " - ")) %>% 
  distinct(comp) %>% mutate(what=map(comp,~matches_by_id(.,"round"))) %>% 
  mutate(long=map_int(what, ~length(.))) %>% 
  filter(long==2) %>% 
  mutate(country=map_chr(what,"country"),
         matches=map(what,"matches")) %>% 
  unnest(matches) -> out_there
out_there %>% anti_join(games,by=c("matches"="match")) %>% arrange(matches) -> j
j
```

this is what I don't already have, so get them:


```{r}
j %>%
  select(match=matches,country) %>% 
  get_games(prefix="sched") -> xy # then combine, above; here is where the sched needs to be checked
xy
stopifnot(nrow(xy)>0)
xy = xy %>% mutate(score=ifelse(str_detect(score," - "),"upcoming",score)) 
xy
saveRDS(xy,"rds/xx.rds")
xy %>% count(country) %>% arrange(desc(n)) %>% print(n=Inf)
xy %>% arrange(time_stamp) %>% View("matches")
beepr::beep(2)
```

update database as below


## get upcoming matches, old method

### initialization (throw away later)

```{r}
#last=tibble(comp=16,last_done=as.Date(0,origin="1970-01-01"))
last_mci=readRDS("rds/last_mci.rds")
```

### get dates to update from today and get comp list

clear mci.* before starting on this
do not clear sched* files? Or only clear old ones?

```{bash}
rm rds/mci*.rds
rm rds/sched*.rds
```



#### by date below

```{r}
today=Sys.time()
today
dtoday=as.Date(today)

tibble(mydates=seq(dtoday-3,dtoday+7,"days")) %>% 
  mutate(comps=map(mydates,date_comps)) %>% 
  unnest() %>% 
  distinct(comps) %>% 
  pull(comps) -> 
dc
last_mci=readRDS("rds/last_mci.rds")
z=tibble(comp=sort(dc)) %>% 
  left_join(last_mci) %>% 
  mutate(is_na=is.na(last_date)) %>% 
  mutate(random=runif(length(dc))) %>% 
  arrange(desc(is_na),last_date,random) %>% 
  mutate(r=row_number())
View(z, "leagues with games")
beepr::beep(2)
```


Investigate `z` and choose `min_get` and `max_get`. Usually `min_get` will be 1, but if the run has failed before, find the most recent ones in `last_mci` and get them again.

```{r}
min_get=1
max_get=49
```

get that many leagues


```{r}
xxx = z %>% 
  slice(min_get:max_get) %>% 
  select(comp)
z2 = xxx %>% mutate(last_date=Sys.time()) %>% 
  bind_rows(last_mci) %>% 
  group_by(comp) %>% 
  summarize(last_date=max(last_date))
saveRDS(xxx,"rds/xxx.rds")
saveRDS(z2,"rds/last_mci.rds")
```

get matches for those leagues: need to not get scores for these

I seem to need to do this twice, matches being NULL the first time (but it works the second, and doesn't take long, because the matches are stored). 
This can be done from command line with mci.R.

```{r, warning=F}
xxx=readRDS("rds/xxx.rds")
xxx %>% 
  mutate(matches=map(comp,matches_by_comp_id)) %>% 
  mutate(istib=map_lgl(matches,is.tibble)) -> dd2 # this distinguishes lists from others
xxx %>% 
  mutate(matches=map(comp,matches_by_comp_id)) %>% 
  mutate(istib=map_lgl(matches,is.tibble)) -> dd2 # this distinguishes lists from others
dd2
beepr::beep(2)
```

### get matches 

```{r}
dd2
last_mci
dd25 = dd2 %>% filter(istib) %>% left_join(last_mci,by=c("comp"="comp")) %>% 
  arrange(!is.na(last_date),last_date)
dd25 %>% count(last_date)
dd25
dd3 = dd25 # %>% slice(1:100) # change this number as appropriate
dd3 = dd3 %>% mutate(last_date=today)
dd3

#games=readRDS("rds/games.rds")
# update last

last = dd3 %>% select(comp,last_date) %>% 
  bind_rows(last_mci) %>% group_by(comp) %>% summarize_all(first)


thing = dd3 %>% 
  unnest() %>% 
  anti_join(games,by=c("matches"="match")) %>% 
  mutate(match=matches) %>% 
  arrange(match)
saveRDS(thing,"rds/thing.rds")
thing
```

### get scheduled matches

```{r warning=F}
thing=readRDS("rds/thing.rds")
thing
thing %>% get_games(prefix="sched") -> xx # then combine, above; here is where the sched needs to be checked
xx
xx = xx %>% mutate(score=ifelse(str_detect(score," - "),"upcoming",score)) 
xx
saveRDS(xx,"rds/xx.rds")
xx %>% count(country) %>% arrange(desc(n)) %>% print(n=Inf)
xx %>% arrange(time_stamp) %>% View("matches")
beepr::beep(2)
```

now go back and update database


## get latest results -------------------------------

get rid of match*.rds files before starting this. 

```{bash}
rm [12]*.html
rm rds/match*.rds
date
```


### games to get---------------

the third arg to `results_to_get` is min number of days back
I've done back to 2000 days (I think this is far enough)

Ideas: 
- randomly choose no-result games from the past to fill in
- randomly (somehow) choose ungotten games to get (eg. ones "next to" games I already got)
- get all games from international comps for predicting world cup (by June), or use pinnacle odds


```{r gg2}
# gg=results_to_get(games,4.0)
min_hours=2.5
max_hours=3
gg=results_to_get(games,max_hours/24,since_hours = min_hours)
#if (nrow(gg)>1000) gg=sample_n(gg,1000)
gg = gg %>% arrange(time_stamp)
View(gg,"matches to get")
saveRDS(gg,"rds/gg.rds")
```

## get them ------------------

this works now (but it fails when the HTML is not downloaded, I think)

```{r xx3,warning=FALSE}
gg=readRDS("rds/gg.rds")
gg %>% get_games() -> xx
saveRDS(xx,"rds/xx.rds")
#xx=get_games(gg)
xx %>% select(-(1:3)) %>% filter(str_detect(score," - ")) %>% unite(comp_full,country,comp_name) %>% 
  arrange(time_stamp) %>% View("results")
# xx %>% filter(str_detect(score," - ")) %>% count(country) %>% arrange(desc(n)) 
xx %>% mutate(is_done=str_detect(score, " - ")) %>% 
  count(is_done)
beepr::beep(2)
```

```{r}
games
```


## get upcoming games

get xx (games that I just got results for): this could stand to be shrunk to the games I actually *got* results for, not just the ones I might have done

```{bash}
rm rds/mci*.rds
rm rds/sched*.rds
```

```{r}
xx=readRDS("rds/xx.rds")
xx %>% filter(str_detect(score, " - ")) %>% 
  distinct(comp) %>% nrow()
```

these are the comps that just had games for which I have results, so they are ripe for getting new ones
if error here, likely no rows

```{r}
xx %>% filter(str_detect(score, " - ")) %>% 
  distinct(comp) %>% mutate(what=map(comp,~matches_by_id(.,"round"))) %>% 
  mutate(long=map_int(what, ~length(.))) %>% 
  filter(long==2) %>% 
  mutate(country=map_chr(what,"country"),
         matches=map(what,"matches")) %>% 
  unnest(matches) -> out_there
out_there %>% anti_join(games,by=c("matches"="match")) %>% arrange(matches) -> j
j
```

this is what I don't already have, so get them:


```{r}
j %>%
  select(match=matches,country) %>% 
  get_games(prefix="sched") -> xy # then combine, above; here is where the sched needs to be checked
xy
stopifnot(nrow(xy)>0)
xy = xy %>% mutate(score=ifelse(str_detect(score," - "),"upcoming",score)) 
xy
saveRDS(xy,"rds/xx.rds")
xy %>% count(country) %>% arrange(desc(n)) %>% print(n=Inf)
xy %>% arrange(time_stamp) %>% View("matches")
beepr::beep(2)
```

update database as below


## get upcoming matches, old method

### initialization (throw away later)

```{r}
#last=tibble(comp=16,last_done=as.Date(0,origin="1970-01-01"))
last_mci=readRDS("rds/last_mci.rds")
```

### get dates to update from today and get comp list

clear mci.* before starting on this
do not clear sched* files? Or only clear old ones?

```{bash}
rm rds/mci*.rds
rm rds/sched*.rds
```



#### by date below

```{r}
today=Sys.time()
today
dtoday=as.Date(today)

tibble(mydates=seq(dtoday-3,dtoday+7,"days")) %>% 
  mutate(comps=map(mydates,date_comps)) %>% 
  unnest() %>% 
  distinct(comps) %>% 
  pull(comps) -> 
dc
last_mci=readRDS("rds/last_mci.rds")
z=tibble(comp=sort(dc)) %>% 
  left_join(last_mci) %>% 
  mutate(is_na=is.na(last_date)) %>% 
  mutate(random=runif(length(dc))) %>% 
  arrange(desc(is_na),last_date,random) %>% 
  mutate(r=row_number())
View(z, "leagues with games")
beepr::beep(2)
```


Investigate `z` and choose `min_get` and `max_get`. Usually `min_get` will be 1, but if the run has failed before, find the most recent ones in `last_mci` and get them again.

```{r}
min_get=1
max_get=49
```

get that many leagues


```{r}
xxx = z %>% 
  slice(min_get:max_get) %>% 
  select(comp)
z2 = xxx %>% mutate(last_date=Sys.time()) %>% 
  bind_rows(last_mci) %>% 
  group_by(comp) %>% 
  summarize(last_date=max(last_date))
saveRDS(xxx,"rds/xxx.rds")
saveRDS(z2,"rds/last_mci.rds")
```

get matches for those leagues: need to not get scores for these

I seem to need to do this twice, matches being NULL the first time (but it works the second, and doesn't take long, because the matches are stored). 
This can be done from command line with mci.R.

```{r, warning=F}
xxx=readRDS("rds/xxx.rds")
xxx %>% 
  mutate(matches=map(comp,matches_by_comp_id)) %>% 
  mutate(istib=map_lgl(matches,is.tibble)) -> dd2 # this distinguishes lists from others
xxx %>% 
  mutate(matches=map(comp,matches_by_comp_id)) %>% 
  mutate(istib=map_lgl(matches,is.tibble)) -> dd2 # this distinguishes lists from others
dd2
beepr::beep(2)
```

### get matches 

```{r}
dd2
last_mci
dd25 = dd2 %>% filter(istib) %>% left_join(last_mci,by=c("comp"="comp")) %>% 
  arrange(!is.na(last_date),last_date)
dd25 %>% count(last_date)
dd25
dd3 = dd25 # %>% slice(1:100) # change this number as appropriate
dd3 = dd3 %>% mutate(last_date=today)
dd3

#games=readRDS("rds/games.rds")
# update last

last = dd3 %>% select(comp,last_date) %>% 
  bind_rows(last_mci) %>% group_by(comp) %>% summarize_all(first)


thing = dd3 %>% 
  unnest() %>% 
  anti_join(games,by=c("matches"="match")) %>% 
  mutate(match=matches) %>% 
  arrange(match)
saveRDS(thing,"rds/thing.rds")
thing
```

### get scheduled matches

```{r warning=F}
thing=readRDS("rds/thing.rds")
thing
thing %>% get_games(prefix="sched") -> xx # then combine, above; here is where the sched needs to be checked
xx
xx = xx %>% mutate(score=ifelse(str_detect(score," - "),"upcoming",score)) 
xx
saveRDS(xx,"rds/xx.rds")
xx %>% count(country) %>% arrange(desc(n)) %>% print(n=Inf)
xx %>% arrange(time_stamp) %>% View("matches")
beepr::beep(2)
```

now go back and update database


## get latest results -------------------------------

get rid of match*.rds files before starting this. 

```{bash}
rm [12]*.html
rm rds/match*.rds
date
```


### games to get---------------

the third arg to `results_to_get` is min number of days back
I've done back to 2000 days (I think this is far enough)

Ideas: 
- randomly choose no-result games from the past to fill in
- randomly (somehow) choose ungotten games to get (eg. ones "next to" games I already got)
- get all games from international comps for predicting world cup (by June), or use pinnacle odds


```{r gg3}
# gg=results_to_get(games,4.0)
min_hours=2.5
max_hours=3
gg=results_to_get(games,max_hours/24,since_hours = min_hours)
#if (nrow(gg)>1000) gg=sample_n(gg,1000)
gg = gg %>% arrange(time_stamp)
View(gg,"matches to get")
saveRDS(gg,"rds/gg.rds")
```

## get them ------------------

this works now (but it fails when the HTML is not downloaded, I think)

```{r xx1,warning=FALSE}
gg=readRDS("rds/gg.rds")
gg %>% get_games() -> xx
saveRDS(xx,"rds/xx.rds")
#xx=get_games(gg)
xx %>% select(-(1:3)) %>% filter(str_detect(score," - ")) %>% unite(comp_full,country,comp_name) %>% 
  arrange(time_stamp) %>% View("results")
# xx %>% filter(str_detect(score," - ")) %>% count(country) %>% arrange(desc(n)) 
xx %>% mutate(is_done=str_detect(score, " - ")) %>% 
  count(is_done)
beepr::beep(2)
```


(first,match_search,n_back)) %>% unnest() %>% 
  anti_join(games,by=c("matches"="match")) %>% 
  mutate(match=matches) %>% 
  mutate(country=NA_character_) %>% 
  get_games() -> xx
xx %>% print(n=Inf)
xx %>% count(comp) -> d
tibble(comp=ll) %>% left_join(d) %>% filter(!is.na(n)) %>% print(n=Inf) # counts how many of the searched-for comps had games found


games %>% arrange(comp,country) %>% print(n=Inf)

# fill in missing matches in a league (that I do not already have)

# experimenting with fill

```{r}
d=tribble(
  ~x, ~y,
  1, "a",
  1, NA,
  1, "a",
  2, "b",
  2, NA,
  2, "b",
  3, NA
)
d %>%  arrange(x,y) %>% group_by(x) %>% fill(y)

games %>% arrange(comp,country) %>% group_by(comp) %>% fill(country) -> ggg
ggg %>% count(country) %>% print(n=Inf)
games=ggg

games %>% group_by(t1) %>% count(country) %>% filter(is.na(country))
games %>% group_by(t1) %>% count(country) %>% filter(t1 %in% c(78,83,87,89))
```




## checking for changes in team names and other junk

```{r}
all_names=function(id,games) {
  games %>% filter(t1==id) %>% count(t1_name)
}
id=1290
all_names(id,games)
games %>% filter(t1==id) %>% arrange(time_stamp) %>% print(n=Inf)

games
games %>% group_by(t1) %>% count(t1_name) %>% count(t1) %>% filter(nn>1) %>% print(n=Inf) %>% 
  mutate(names=map(t1,all_names,games)) %>% unnest() %>% print(n=Inf)
```

dc = comps to get

```{r}
leagues %>% filter(level==99) %>% pull(comp) -> dc
tibble(comp=dc) %>% mutate(matches=map(comp,matches_by_id_tibble,"round")) %>%  # print(n=Inf)
  unnest() %>% 
  anti_join(games,by=c("matches"="match")) %>% 
  mutate(match=matches) %>% get_games() -> xx # then combine, above
xx %>% select(-(1:3))
xx %>% count(country) %>% arrange(n) %>% print(n=Inf)
```


## thinking about missing games

```{r}
games
```

sort by match and diff from previous

ideas from <https://stackoverflow.com/questions/39176855/find-difference-between-rows-by-id-but-place-difference-on-first-row-in-r?rq=1>

```{r}
suggested = games %>%  arrange(match) %>% 
  mutate(diff=match-lag(match)) %>% 
  mutate(diffl=lead(match)-match) %>% 
  mutate(md=pmax(diff,diffl)) %>% 
  select(match,diff,diffl,md) %>% 
  mutate(suggest=case_when(
    diff>1 ~ match-1,
    diffl>1 ~ match+1,
    TRUE ~ NA_real_)) %>% 
  filter(suggest>2000000)
View(suggested)
```

get rid of old ones

```{bash}
rm rds/sched*.rds
```

get sample first

```{r}
nsamp=1000
gg = suggested %>% mutate(country=NA_character_) %>% 
  mutate(gotmatch=match,
         match=suggest) %>% 
  sample_n(nsamp) 
gg
saveRDS(gg,"rds/suggested.rds")
```


construct a data frame for get_games

```{r}
gg %>% 
  get_games(prefix="sched") %>% 
  filter(t1>0)
xx
saveRDS(xx,"rds/xx.rds")
```

go back to "update database" to add these on, or:

```{r}
games=combine2(games,xx) 
saveRDS(games,"games.rds")
```


can I get country from `comp_name`?

```{r}
games %>% group_by(comp,comp_name) %>% count(country)
```

to make a lookup table



## fixing up Scotland

```{r}
games %>% filter(comp==41506) %>% arrange(desc(time_stamp))
```

```{r}
games %>% filter(match!=2473979) -> games
```


## fixing up character problem from downloading matches in RScript

### create normal forms

idea: 
- get a normal-form version of games, teams, leagues
- find most common names
- reconstitute games

Save games first

```{r}
saveRDS(games,"rds/games.rds")
```

warnings, if any: uninitialized col n?

read back, for checking

```{r}
g2=readRDS("rds/games.rds")
g2 %>% filter(comp==41514)
```

Seems to work.

```{r}
names(games)
```

`top_n` key for later.

Normal form:

```{r}
match = games %>% select(match,t1,t2,comp,score,time_stamp,retrieved)
```

```{r}
team1=games %>% select(t1,t1_name) %>% rename(id=t1,name=t1_name)
team1
team2=games %>% select(t2,t2_name) %>% rename(id=t2,name=t2_name)
team=bind_rows(team1,team2)
team
```

```{r}
comp = games %>% select(comp,comp_name,country)
```

### handle comps first

first handle country of comp

```{r}
comp_country = comp %>% group_by(comp) %>% count(country) %>% arrange(desc(n)) %>% top_n(1) %>% select(-n)
```

comp names

```{r}
comp_name = comp %>% group_by(comp) %>% count(comp_name) %>% arrange(desc(n)) %>% top_n(1) %>% select(-n)
comp_name
```

### now handle teams

```{r}
team_name = team %>% group_by(id) %>% count(name) %>% arrange(desc(n)) %>% top_n(1) %>% select(-n)
```

```{r}
names(games)
games = match %>% left_join(team_name,by=c("t1"="id")) %>% rename(t1_name=name) %>% 
  left_join(team_name,by=c("t2"="id")) %>% rename(t2_name=name) %>% 
  left_join(comp_country) %>% 
  left_join(comp_name)
saveRDS(games,"rds/games.rds")
```

## all the fixup code

```{r fixup}
saveRDS(games,"rds/games2.rds")
match = games %>% select(match,t1,t2,comp,score,time_stamp,retrieved)
team1=games %>% select(t1,t1_name) %>% rename(id=t1,name=t1_name)
team2=games %>% select(t2,t2_name) %>% rename(id=t2,name=t2_name)
team=bind_rows(team1,team2)
comp = games %>% select(comp,comp_name,country)
comp_country = comp %>% group_by(comp) %>% count(country) %>% arrange(desc(n)) %>% top_n(1) %>% select(-n)
comp_name = comp %>% group_by(comp) %>% count(comp_name) %>% arrange(desc(n)) %>% top_n(1) %>% select(-n)
team_name = team %>% group_by(id) %>% count(name) %>% arrange(desc(n)) %>% top_n(1) %>% select(-n)
games = match %>% left_join(team_name,by=c("t1"="id")) %>% rename(t1_name=name) %>% 
  left_join(team_name,by=c("t2"="id")) %>% rename(t2_name=name) %>% 
  left_join(comp_country) %>% 
  left_join(comp_name)
saveRDS(games,"rds/games.rds")
```

#### find stuff

```{r}
games %>% filter(t1==1242) %>% arrange(time_stamp)
```

## remove wrong scores

```{r}
game_list=2801777:2801802
game_list
```

```{r}
games %>% mutate(score=ifelse(match %in% game_list, "upcoming", score)) %>% 
  saveRDS("rds/games.rds")
```

```{r}
games %>% filter(comp==48274)
```


## get matches that were missed before

are they there or missing?

```{r}
country="England"
matches=2801777:2801802
games %>%  filter(match %in% matches)
```


Input is country and vector of match numbers

```{r}
thing=tibble(country=country, match=matches)
thing
saveRDS(thing, "rds/thing.rds")
```

now go to "get scheduled matches" in get upcoming matches




## re-get TBA matches (at some space from previous get) --------------------

## check matches where retrieved is too soon after kickoff: delete and re-get

## england championship blank and reget

```{r}
games %>% filter(comp==48274) %>% arrange(desc(time_stamp)) %>% 
  filter(between(match, 2801979, 2802000))
```

those; set score to 17:00

```{r}
games %>% mutate(score=case_when(
  comp==48274 & between(match, 2801977, 2802000) ~ "17:00",
  TRUE                                           ~ score
)) -> games
```

save

```{r}
saveRDS(games, "rds/games.rds")
```

## get desired competitions


create dc with comp ids, then go back to 3.

```{r}
dc=c(119)
```

try this in get upcoming games, old version