###### pancake

this is subsumed in above

Investigate `z` and choose `min_get` and `max_get`. Usually `min_get` will be 1, but if the run has failed before, find the most recent ones in `last_mci` and get them again.

```{r}
min_get=1
max_get=5
```

get that many leagues


```{r}
xxx = z %>% 
  slice(min_get:max_get) %>% 
  select(comp)
z2 = xxx %>% mutate(last_date=Sys.time()) %>% 
  bind_rows(last_mci) %>% 
  group_by(comp) %>% 
  summarize(last_date=max(last_date))
saveRDS(xxx,"rds/xxx.rds")
saveRDS(z2,"rds/last_mci.rds")
```

get matches for those leagues

I seem to need to do this twice, matches being NULL the first time (but it works the second, and doesn't take long, because the matches are stored). 
This can be done from command line with mci.R.

```{r, warning=F}
xxx=readRDS("rds/xxx.rds")
xxx %>% 
  mutate(matches=map(comp,matches_by_comp_id)) %>% 
  mutate(istib=map_lgl(matches,is.tibble)) -> dd2 # this distinguishes lists from others
xxx %>% 
  mutate(matches=map(comp,matches_by_comp_id)) %>% 
  mutate(istib=map_lgl(matches,is.tibble)) -> dd2 # this distinguishes lists from others
dd2
beepr::beep(2)
```

### get matches 

```{r}
dd2
last_mci
dd25 = dd2 %>% filter(istib) %>% left_join(last_mci,by=c("comp"="comp")) %>% 
  arrange(!is.na(last_date),last_date)
dd25 %>% count(last_date)
dd25
dd3 = dd25 # %>% slice(1:100) # change this number as appropriate
dd3 = dd3 %>% mutate(last_date=today)
dd3

#games=readRDS("rds/games.rds")
# update last

last = dd3 %>% select(comp,last_date) %>% 
  bind_rows(last_mci) %>% group_by(comp) %>% summarize_all(first)


thing = dd3 %>% 
  unnest() %>% 
  anti_join(games,by=c("matches"="match")) %>% 
  mutate(match=matches) %>% 
  arrange(match)
saveRDS(thing,"rds/thing.rds")
thing
```

### get scheduled matches

```{r warning=F}
thing=readRDS("rds/thing.rds")
thing
thing %>% get_games(prefix="sched") -> xx # then combine, above; here is where the sched needs to be checked
xx
saveRDS(xx,"rds/xx.rds")
xx %>% count(country) %>% arrange(desc(n)) %>% print(n=Inf)
xx %>% arrange(time_stamp) %>% View("matches")
beepr::beep(2)
```

now go back and update database
