---
title: "Scoresway Notebook"
output: html_notebook
---

## 1. Packages & functions

```{r one, message=F}
library(tidyverse)
library(rvest)
library(anytime)
library(lubridate)
library(RCurl)
source("functions.R")
```



## 2. get upcoming games

get xx (games that I just got results for): this could stand to be shrunk to the games I actually *got* results for, not just the ones I might have done

```{bash}
rm rds/mci*.rds
rm rds/sched*.rds
```

```{r two}
xx=readRDS("rds/xx.rds")

```

these are the comps that just had games for which I have results, so they are ripe for getting new ones
if error here, likely no rows

```{r}
xx %>% filter(str_detect(score, " - ")) %>% 
  distinct(comp) %>% 
  arrange(comp) %>% 
  mutate(what=map(comp,~matches_by_id(.,"round"))) %>% 
  mutate(long=map_int(what, ~length(.))) %>% 
  filter(long==2) %>% 
  mutate(country=map_chr(what,"country"),
         matches=map(what,"matches")) %>% 
  unnest(matches) -> out_there
out_there %>% anti_join(games,by=c("matches"="match")) %>% arrange(matches) -> j
View(j, "matches to get")
j %>%
  select(match=matches,country) %>% 
  get_games(prefix="sched") -> xy # then combine, above; here is where the sched needs to be checked
xy
stopifnot(nrow(xy)>0)
saveRDS(xy,"rds/xx.rds")
xy %>% count(country) %>% arrange(desc(n)) %>% print(n=Inf)
xy %>% arrange(time_stamp) %>% View("matches")
beepr::beep(2)
```

go to 6.


## 3. get upcoming matches, old method

### initialization (throw away later)

```{r three}
#last=tibble(comp=16,last_done=as.Date(0,origin="1970-01-01"))
last_mci=readRDS("rds/last_mci.rds")
```

### get dates to update from today and get comp list

clear mci.* before starting on this
do not clear sched* files? Or only clear old ones?

```{bash}
rm rds/mci*.rds
rm rds/sched*.rds
```



#### by date below. 

Reorganized to do in one shot. Choose leagues to get up top. (corrected error re comps not seen before)

```{r}
min_get=1
max_get=200
today=Sys.time()
today
dtoday=as.Date(today)
back=3
forward=7
tibble(mydates=seq(dtoday-back,dtoday+forward,"days")) %>% 
  mutate(comps=map(mydates,date_comps)) %>% 
  unnest() %>% 
  distinct(comps) %>% 
  pull(comps) -> dc
sort(dc)
last_mci=readRDS("rds/last_mci.rds")
now=Sys.time()
tibble(comp=sort(dc)) %>% 
  left_join(last_mci) %>% 
  mutate(is_na=is.na(last_date)) %>% 
  mutate(random=runif(nrow(.))) %>% 
  arrange(desc(is_na),last_date,random) %>% 
  mutate(r=row_number()) %>% 
  mutate(days_ago=(now-last_date)/ddays(1)) -> z
z
z %>% 
  slice(min_get:max_get) %>% 
  filter(days_ago>1 | is.na(days_ago)) %>% 
  select(comp) -> xxx
xxx
stopifnot(nrow(xxx)>0)
z2 = xxx %>% mutate(last_date=Sys.time()) %>% 
  bind_rows(last_mci) %>% 
  group_by(comp) %>% 
  summarize(last_date=max(last_date))
z2
saveRDS(xxx,"rds/xxx.rds")
saveRDS(z2,"rds/last_mci.rds")
xxx=readRDS("rds/xxx.rds")
xxx %>% 
  mutate(matches=map(comp,matches_by_comp_id)) %>% 
  mutate(istib=map_lgl(matches,is.tibble)) -> dd2 # this distinguishes lists from others
xxx %>% 
  mutate(matches=map(comp,matches_by_comp_id)) %>% 
  mutate(istib=map_lgl(matches,is.tibble)) -> dd2 # this distinguishes lists from others
dd2
dd2
last_mci
dd25 = dd2 %>% filter(istib) %>% left_join(last_mci,by=c("comp"="comp")) %>% 
  arrange(!is.na(last_date),last_date)
dd25 %>% count(last_date)
dd25
dd3 = dd25 # %>% slice(1:100) # change this number as appropriate
dd3 = dd3 %>% mutate(last_date=today)
dd3
last = dd3 %>% select(comp,last_date) %>% 
  bind_rows(last_mci) %>% group_by(comp) %>% summarize_all(first)
thing = dd3 %>% 
  unnest() %>% 
  anti_join(games,by=c("matches"="match")) %>% 
  mutate(match=matches) %>% 
  arrange(match)
saveRDS(thing,"rds/thing.rds")
thing
thing %>% get_games(prefix="sched") -> xx # then combine, above; here is where the sched needs to be checked
xx
saveRDS(xx,"rds/xx.rds")
xx %>% count(country) %>% arrange(desc(n)) %>% print(n=Inf)
xx %>% arrange(time_stamp) %>% View("matches")
beepr::beep(2)
```

now update database: go to 6.



## 4. get latest results 

get rid of match*.rds files before starting this. 

```{bash}
rm [12]*.html
rm rds/match*.rds
date
```


### games to get

the third arg to `results_to_get` is min number of days back
I've done back to 2000 days (I think this is far enough)

Ideas: 
- randomly choose no-result games from the past to fill in
- randomly (somehow) choose ungotten games to get (eg. ones "next to" games I already got)
- get all games from international comps for predicting world cup (by June), or use pinnacle odds


```{r four-gg1}
# gg=results_to_get(games,4.0)
min_hours=2.5
max_hours=4

gg=results_to_get(games,max_hours/24,since_hours = min_hours)
#if (nrow(gg)>1000) gg=sample_n(gg,1000)
gg = gg %>% arrange(time_stamp)
# View(gg,"matches to get")
saveRDS(gg,"rds/gg.rds")
```

## 5. get them 

this works now (but it fails when the HTML is not downloaded, I think)

```{r five,warning=FALSE}
gg=readRDS("rds/gg.rds")
gg %>% arrange(match) -> gg
View(gg, "matches to get")
gg %>% get_games() -> xx
saveRDS(xx,"rds/xx.rds")
#xx=get_games(gg)
xx %>% select(-(1:3)) %>% filter(str_detect(score," - ")) %>% unite(comp_full,country,comp_name) %>% 
  arrange(time_stamp) %>% View("results")
# xx %>% filter(str_detect(score," - ")) %>% count(country) %>% arrange(desc(n)) 
xx %>% mutate(is_done=str_detect(score, " - ")) %>% 
  count(is_done)
beepr::beep(2)
```


## 6. update database

```{r, six-update-database}
games=readRDS("rds/games.rds")
xx=readRDS("rds/xx.rds")
games %>% mutate(is_res=has_result(score)) %>%  count(is_res) -> d1
games=combine2(games,xx) 
saveRDS(games,"rds/games.rds")
games %>% mutate(is_res=has_result(score) ) %>%  count(is_res) %>% bind_rows(d1, .id="which") -> d
d %>% pull(n) -> nn
tribble(
  ~what, ~count,
  "total games", nn[1]+nn[2],
  "new scores", nn[2]-nn[4],
  "new games without scores", nn[1]-nn[3]
)
```

can go to 2. now if gained new scores



## 7. get old ungotten games

think about retrieving games without scores that I haven't checked in the longest (at least a day)

get rid of match*.rds files before starting this. 

```{bash}
rm [12]*.html
rm rds/match*.rds
date
```

```{r seven}
now=Sys.time()
games %>% filter(score!="Cancelled", !(comp %in% c(43429,43430,49540,49542))) %>% 
  filter(!str_detect(score," - ")) %>% 
  filter(t1>0) %>% 
  mutate(since_ko=as.period(now-time_stamp)/hours(1)) %>% 
  filter(since_ko>3) %>%
#  mutate(since_ret=(now-retrieved)/ddays(1)) %>% 
#  filter(since_ret>0.75) %>% 
  mutate(num=as.period(now-time_stamp)/hours(1),
         den=as.period(retrieved-time_stamp)/hours(1),
         ratio=as.numeric(num)/as.numeric(den)) %>%
  filter(ratio<0 | ratio>2) %>% 
  arrange(ratio) %>% 
  mutate(row=row_number()) -> gg
saveRDS(gg,"rds/gg.rds")
```


go back to "5. get them" above, then come down to "6. update database"



## 8. get "upcoming" games

get rid of match*.rds files before starting this. 

```{bash}
rm [12]*.html
rm rds/match*.rds
date
```

```{r eight}
now=Sys.time()
(games %>% filter(score=="upcoming") %>% 
  filter(t1>0) %>% 
  mutate(since=as.duration(now-time_stamp)/dminutes(1)) %>%
  mutate(avail=(since>180)) %>% 
  filter(avail) %>% 
  arrange(retrieved) -> gg)
```


decide how many to get

```{r}
n1get=1
n2get=2000
n2get=ifelse(n2get>nrow(gg), nrow(gg), n2get)
n2get
gg %>% slice(n1get:n2get) -> gg
saveRDS(gg,"rds/gg.rds")
```

go back to "5. get them" above, then come down to "6. update database"

get## 9. remove compless games

save game numbers to get again

```{r nine}
nrow(games)
games %>% filter(comp<=0) -> reget
games %>% filter(comp>0) %>% saveRDS("rds/games.rds")
games=readRDS("rds/games.rds") 
games %>% nrow()
```

### reget

```{bash}
rm [12]*.html
rm rds/match*.rds
```

```{r}
reget %>% pull(match) %>% enframe()
```


```{r}
reget %>% get_games() -> xx
saveRDS(xx,"rds/xx.rds")
xx
```

```{r}
xx %>% count(comp>0)
```


go to 6.

## 10. reget TBAs

```{bash}
rm [12]*.html
rm rds/match*.rds
```

```{r ten}
my_since=2.5 # days
now=Sys.time()
games %>% filter(score=="TBA") %>% 
  mutate(since=(now-retrieved)/ddays(my_since)) %>% 
  filter(since>my_since) -> tbas
tbas %>% pull(match) %>% enframe()
```




go to 6. after this is done

```{r}
tbas %>% get_games() -> xx
saveRDS(xx,"rds/xx.rds")
xx %>% mutate(what=case_when(
  score=="TBA" ~ "tba",
  str_detect(score, ":") ~ "kickoff",
  TRUE ~ "score"
)) %>% count(what)
```

goto 6. update database.

## 11. unget games with too little time between timestamp and retrieved

all games gotten after less than 2.5 hours turned back to a fake time (hopefully searchable)

```{r eleven}
games %>% mutate(diff=(retrieved-time_stamp)/dhours(1)) %>% 
  mutate(has_result=str_detect(score," - ")) %>% 
  mutate(since=case_when(
    !has_result ~ 1e10,
    TRUE        ~ diff
  )) %>% 
  mutate(score=ifelse(since<2.5, "00:16", score)) %>% 
  select(-diff, -has_result, -since) -> games
saveRDS(games, "rds/games.rds")
```

```{r}
games %>% filter(score=="00:16") %>% select(country:retrieved)
```

## 12. get games from specific comps (eg. at start of season)

```{r}
comp=c(53516)
tibble(comp) %>% 
  mutate(what=map(comp,~matches_by_id(.,"round"))) %>% 
  mutate(long=map_int(what, ~length(.))) %>% 
  filter(long==2) %>% 
  mutate(country=map_chr(what,"country"),
         matches=map(what,"matches")) %>% 
  unnest(matches) -> out_there
out_there %>% anti_join(games,by=c("matches"="match")) %>% arrange(matches) -> j
View(j, "matches to get")
j %>%
  select(match=matches,country) %>% 
  get_games(prefix="sched") -> xy # then combine, above; here is where the sched needs to be checked
xy
stopifnot(nrow(xy)>0)
saveRDS(xy,"rds/xx.rds")
xy %>% count(country) %>% arrange(desc(n)) %>% print(n=Inf)
xy %>% arrange(time_stamp) %>% View("matches")
beepr::beep(2)
```

go to 6.


Testing

```{r}
games %>% filter(t1_name=="Côte d'Ivoire")

```

